Gächter et al (2007, JPE) replication

### 2021-04-06 reports/replication.Rmd
misc

---
title: "Gächter et al (2007, JPE) replication"
description: |
  A new article created using the Distill format.
author:
  - name: Hauke Roggenkamp 
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

@@

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree]. The current demo version of the experiments can be found [here](https://cliccs.herokuapp.com/).^[Some of the demo experiments will model three-player games as this is the maximum number of players one can open in split-screen mode.] One of these experiments will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances) to allow for comparisons. I'll therefore run seesions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of 20 points and a group account with a return of $1.5$, such that:
$$
N_i^{t+1}=N-i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
$$

@@

```{r}

gaechter <- noPunish10[order(gr_id, per),
           .(treatment = "noPunish10", 
             groupID = gr_id, 
             round = per,
             contribution = sum,
             endowment = gdp,
             share = mean,
             stock = gdp + ceiling(sum/4*1.5)*4-sum,
             gain = ceiling(sum/4*1.5)*4-sum,
             bot_active = 0)] %>% unique()

gaechter %>%
  head(n = 12) %>%
  kbl() %>% 
  # scroll_box(height = "200px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)
```

>>>>

---
title: "Gächter et al (2007, JPE) replication"
description: |
  Reproducing Gächter et al.'s Visualizations.
author:
  - name: Hauke Roggenkamp 
    affiliation: CLICCS
    affiliation_url: https://www.cliccs.uni-hamburg.de/
date: "`r Sys.Date()`"
bibliography: biblio.bib
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: false
    code_folding: true
---

@@

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree]. The current demo version of the experiments can be found [here](https://cliccs.herokuapp.com/).^[Some of the demo experiments will model three-player games as this is the maximum number of players one can open in split-screen mode.] One of these experiments will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances) to allow for comparisons. I'll therefore run sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of 20 points and a group account with a return of $1.5$, such that:
$$
N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
$$

@@

```{r writeData}

gaechter <- noPunish10[order(gr_id, per),
           .(treatment = "noPunish10", 
             groupID = gr_id, 
             round = per,
             contribution = sum/4,
             endowment = gdp/4,
             share = mean,
             stock = (gdp + ceiling(sum/4*1.5)*4-sum)/4,
             gain = (ceiling(sum/4*1.5)*4-sum)/4,
             bot_active = 0,
             disaster = 0,
             EWE = 0,
             noComprehension = 0)] %>% unique()

gaechter %>%
  head(n = 12) %>%
  kbl() %>% 
  # scroll_box(height = "200px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

save(gaechter, file = "../data/processed/gaechter2017.rda")
write.csv(gaechter, file ="../data/processed/gaechter2017.csv")
